STA302 Final Project Proposal

### 2024-11-27 paper/proposal.Rmd
Removed 'owners' from pairplot and made owners and owners_combined factored columns

model <- lm(average_playtime ~ price + positive_ratings + negative_ratings + developer + owners, data=data)
```
## Create Response vs Fitted Scatterplot to check patterns in residuals before further analysis.
```{r}
#| echo: false
#| warning: false
#| message: false
y_hat <- fitted(model)
plot(x = y_hat, y = data$average_playtime, main = "Response vs. Fitted", xlab = "Fitted", ylab = "Average Playtime")
abline(a=0, b=1, lty=2)
```
## Create Pairwise Scatterplots for Predictors to look for multicollinearity
```{r}
#| echo: false
#| warning: false
#| message: false
ggpairs(data[, c(6, 7, 10, 11)])

>>>>

model <- lm(average_playtime ~ price + positive_ratings + negative_ratings + developer + owners, data=data)
```
## Create Response vs Fitted Scatterplot to check patterns in residuals before further analysis.
```{r}
#| echo: false
#| warning: false
#| message: false
y_hat <- fitted(model)
plot(x = y_hat, y = data$average_playtime, main = "Response vs. Fitted", xlab = "Fitted", ylab = "Average Playtime")
abline(a=0, b=1, lty=2)
```
## Create Pairwise Scatterplots for Predictors to look for multicollinearity
```{r}
#| echo: false
#| warning: false
#| message: false

ggpairs(data[, c(6, 7, 11)]) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
        axis.text.y = element_text(size = 8))
